---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ggecdf

<!-- badges: start -->
<!-- badges: end -->

The goal of ggecdf is to easily create weighted and unweighted empirical cumulative distributions (ECDFs) in ggplot2

## Installation

You can install the development version of ggecdf from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("malcolmbarrett/ggecdf")
```

## Example

`geom_ecdf()` allows you to create ECDFs based on ggplot's `stat_ecdf()`

```{r example1}
library(ggecdf)
library(ggplot2)
# dataset with weights
nhefs_weights <- tidysmd::nhefs_weights

ggplot(
  nhefs_weights,
  aes(x = smokeyrs, color = factor(qsmk))
) +
  geom_ecdf() +
  xlab("Smoking Years") +
  ylab("Proportion <= x (unweighted)")
```

Additionally, `geom_ecdf()` supports a `weights` aesthetic to calculate weighted ECDFs. For instance, here's the same variables weighted by an ATO weight:

```{r example2}
ggplot(
  nhefs_weights,
  aes(x = smokeyrs, color = factor(qsmk))
) +
  geom_ecdf(aes(weights = w_ato)) +
  xlab("Smoking Years") +
  ylab("Proportion <= x (weighted)")
```


